---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
library(magrittr)
knitr::opts_chunk$set(
    collapse = TRUE,
    comment = "#>",
    fig.path = "README-"
)
```

[![Build Status](https://travis-ci.com/bilnash/CSE.svg?branch=master)](https://travis-ci.com/bilnash/CSE)

# CSE

The goal of CSE (Casablanca Stock Exchange) is to simplify financial programming workflow with Casablanca stock exchange data.

Currently, it implements 3 mains functions:

- `listed_symbols`: Returns all listed symbols (stocks, indexes, or both) in Casablanca stock exchange.

- `get_symbol`: Returns a symbol historical data corresponding to a specific date range.

- `ipo_date`: Returns a symbol IPO (Initial Public Offering) date.

## Installation

You can install CSE from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("bilnash/CSE", build_vignettes = TRUE)
```

## Documentation

A detailled documentation can be found in the package vignette. 

```{r documentation, eval = FALSE}
vignette("cse_vignette", package = "CSE")
```

## Example

This is a basic example which shows you how to use CSE:

```{r listed_stocks, warning=FALSE}
listed_stocks <- CSE::listed_symbols(type = "stock")
available_indexes <- CSE::listed_symbols(type = "index")

head(listed_stocks)

head(available_indexes)
```

```{r historical_stocks, warning=FALSE}
cosumar_data <- CSE::get_symbol(symbol = "COSUMAR", from = "2018-01-01", to = "2018-06-30", type = "stock")

masi_data <- CSE::get_symbol(symbol = "MASI", from = "2018-01-01", to = "2018-06-30", type = "index")

head(cosumar_data) 

head(masi_data)

```
