---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
library(magrittr)
knitr::opts_chunk$set(
    collapse = TRUE,
    comment = "#>",
    fig.path = "README-"
)
```

[![Project Status: Moved to https://github.com/bilnash/RCSE – The project has been moved to a new location, and the version at that location is no longer working due to changes in Casablanca Stock Exchange API.](https://www.repostatus.org/badges/latest/moved.svg)](https://www.repostatus.org/#moved)

# <span style="color:red">Warning:</span> The project has been moved to a new location, and the version at that location is no longer working due to changes in Casablanca Stock Exchange API. New version is available at [[https://github.com/bilnash/RCSE](https://github.com/bilnash/RCSE)

# CSE

The goal of CSE (Casablanca Stock Exchange) is to simplify financial programming workflow with Casablanca stock exchange data.

Currently, it implements 3 mains functions:

- `listed_symbols`: Returns all listed symbols (stocks, indexes, or both) in Casablanca stock exchange.

- `get_symbol`: Returns a symbol historical data corresponding to a specific date range.

- `ipo_date`: Returns a symbol IPO (Initial Public Offering) date.

## Installation

You can install CSE from github with:

* Quick Installation without vignette:    

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("bilnash/CSE", build_vignettes = FALSE)
```
* Installation with vignette:    

```{r gh-installation2, eval = FALSE}
# install.packages("devtools")
devtools::install_github("bilnash/CSE", build_vignettes = TRUE)
```

## Documentation

Please refer to the package vignette: 

```{r documentation, eval = FALSE}
vignette("cse_vignette", package = "CSE")
```

Also available at: https://bilnash.github.io/CSE/vignettes/cse_vignette.html

## Basic Example

This is a basic example which shows you how to use CSE:

```{r listed_stocks}
listed_stocks <- CSE::listed_symbols(type = "stock")

available_indexes <- CSE::listed_symbols(type = "index")
```

```{r, eval=FALSE}
sample(listed_stocks, size = 6L)
```

```{r, echo=FALSE}
sample(listed_stocks, size = 6L) %>%
    dplyr::tibble(Stock = .) %>%
    knitr::kable()
```

```{r, eval=FALSE}
head(available_indexes)
```

```{r, echo=FALSE}
head(available_indexes) %>%
    knitr::kable()
```

```{r historical_stocks}
cosumar_data <- CSE::get_symbol(symbol = "COSUMAR", from = "2015-01-01", to = "2021-09-29", 
                                type = "stock", format.as.xts = FALSE)

masi_data <- CSE::get_symbol(symbol = "MASI", from = "2015-01-01", to = "2021-09-29", 
                             type = "index", format.as.xts = FALSE)
```

```{r, eval=FALSE}
head(cosumar_data)
```

```{r, echo=FALSE}
head(cosumar_data) %>%
    knitr::kable()
```

```{r, eval=FALSE}
tail(masi_data)
```

```{r, echo=FALSE}
tail(masi_data) %>%
    knitr::kable()
```
