---
title: "CSE Package"
author: "Bilal ELMSILI"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{CSE Package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
library(magrittr)
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The goal of CSE (Casablanca Stock Exchange) is to simplify financial programming workflow with Casablanca stock exchange data.

Currently, it implements 3 mains functions:

- `listed_symbols`: Returns all listed symbols (stocks, indexes, or both) in Casablanca stock exchange.

- `get_symbol`: Returns a symbol historical data corresponding to a specific date range.

- `ipo_date`: Returns a symbol IPO (Initial Public Offering) date.

## Quick Demo

### Firms currently listed in Casablanca stock exchange

```{r, warning=FALSE}
all_stocks <- CSE::listed_symbols(type = "stock")
all_stocks %>% length()
```

```{r, warning=FALSE, eval=FALSE}
dplyr::tibble(Firm = all_stocks) %>%
    head(n = 10)
```

```{r, warning=FALSE, echo=FALSE}
dplyr::tibble(Firm = all_stocks) %>%
    head(n = 10) %>%
    knitr::kable()
```

### Available indexes

```{r, warning=FALSE}
all_indexes <- CSE::listed_symbols(type = "index")
all_indexes %>% nrow()
```

```{r, warning=FALSE, eval=FALSE}
all_indexes %>%
    head(n = 10)
```

```{r, warning=FALSE, echo=FALSE}
all_indexes %>%
    head(n = 10) %>%
    knitr::kable()
```

### IPO Dates

```{r, warning=FALSE}
firm_sample <- all_stocks %>% 
    sample(size = 5)

ipo_dates <- firm_sample %>%
    purrr::map(CSE::ipo_date)
```

```{r, warning=FALSE, eval=FALSE}
dplyr::tibble(Firm = firm_sample, IPO_Date = do.call(c, ipo_dates))
```

```{r, warning=FALSE, echo=FALSE}
dplyr::tibble(Firm = firm_sample, IPO_Date = do.call(c, ipo_dates)) %>%
    knitr::kable()
```

### Get Some Historical Data

```{r, warning=FALSE}
iam <- CSE::get_symbol("ITISSALAT AL-MAGHRIB", "2016-01-01", "2021-09-29", type = "stock")
masi <- CSE::get_symbol("MASI", "2016-01-01", "2021-09-29", type = "index")
```

```{r, warning=FALSE}
dim(iam)
```

```{r, warning=FALSE}
dim(masi)
```

```{r, warning=FALSE}
xts::first(iam, n = 5)
```

```{r, warning=FALSE}
xts::last(iam, n = 5)
```

```{r, warning=FALSE}
xts::first(masi, n = 5)
```

```{r, warning=FALSE}
xts::last(masi, n = 5)
```

```{r, fig.width=7.5, fig.height=5, warning=FALSE}
plot(masi, main = "MASI Historical Values")
plot(iam$Adjusted, main = "IAM Historical Adjusted Prices")
```
